---
output: html_document
editor_options: 
  chunk_output_type: console
---
First, let's look at the different variables, compute new relevant ones and tidy up.

The proportion of each group in the dataset, in a table and then barchart. This part will 
focus on each varialbe individually, and specifically categorial data. 
```{r}
dataset$Type %>% table %>% prop.table()
ggplot(dataset, aes(Type)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Gender %>% table %>% prop.table()
ggplot(dataset, aes(Gender)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Breed1 %>% table %>% prop.table()
ggplot(dataset, aes(Breed1)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Color1 %>% table %>% prop.table()
ggplot(dataset, aes(Color1)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')
ggplot(dataset, aes(Color2)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')
ggplot(dataset, aes(Color3)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$MaturitySize %>% table %>% prop.table()
ggplot(dataset, aes(MaturitySize)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$FurLength %>% table %>% prop.table()
ggplot(dataset, aes(FurLength)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Vaccinated %>% table %>% prop.table()
ggplot(dataset, aes(Vaccinated)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Dewormed %>% table %>% prop.table()
ggplot(dataset, aes(Dewormed)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Sterilized %>% table %>% prop.table()
ggplot(dataset, aes(Sterilized)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$Health %>% table %>% prop.table()
ggplot(dataset, aes(Health)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$State %>% table %>% prop.table()
ggplot(dataset, aes(State)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')

dataset$y %>% table %>% prop.table()
ggplot(dataset, aes(y)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ylab('Proportion')  # Almost no cases of 0. We need to take this into consideration when we split into Train and Validation

```

Now the numeric variables. I'm not sure it's really good to show these with Histograms, as they are integers, but whatever. It gives the general idea.
```{r}
hist(dataset$Age,prob=T, main='Age',xlab = 'Age',col="grey")
lines(density(dataset$Age),col="blue",lwd=2) # Some of the outliers here are disturbing. We will remove them and create this again later

hist(dataset$Quantity,prob=TRUE, main='Quantity',xlab = 'Quantity',col="grey")
lines(density(dataset$Quantity),col="blue",lwd=2) #Same here. let's see exactly how many we have above 8

dataset[Quantity > 8, .N,] # only 49, out of 7684. We'll need to decide what to do with these profiles. 
dataset[Quantity == 1, .N/7684,] # i think we shuld focus on the pets that not in groups and do the prediction on them.
dataset[Quantity > 1 & dataset$y > 1, .N/7684,] #test to see how much goupe pets DONT get adopted
dataset[Quantity == 1 & dataset$y > 1, .N/7684,] #test for the amount of NOT adopted pets that come in group of one.

hist(dataset$Fee,prob=TRUE, main='Fee',xlab = 'Fee',col="grey")
lines(density(dataset$Fee),col="blue",lwd=2) # This is also problematic. Most are zeroes and then disperesed. We'll probably be best to create a binary variable indicating a fee existed

dataset[Fee == 0 , .N/7684,] # 84.1% of pets in the dataset Don't have adoption fees.
dataset[Fee <= 100 , .N/7684,]


hist(dataset$VideoAmt,prob=T, main='Amount of Videos',xlab = 'Videos',col="grey")
lines(density(dataset$VideoAmt),col="blue",lwd=2) #Also here, most profiles have 0 videos. Might be better as a binary variable indicating the existent of videos 

dataset[VideoAmt == 0 , .N/7684,] # 96.3% of pets in the dataset have 0 videos in their profiles. 
dataset[VideoAmt != 0 & dataset$y <=1 , .N/7684,]


hist(dataset$PhotoAmt,prob=TRUE, main='Amount of Photos',xlab = 'Videos',col="grey")
lines(density(dataset$PhotoAmt),col="blue",lwd=2) #This is more interesting. Seems like you usually have 1 picture, but it is rather common to have more. 


dataset[PhotoAmt > 1 & dataset$y <2, .N/7684,]


dataset[PhotoAmt == 1 , .N/7684,]
dataset[PhotoAmt == 2 , .N/7684,]
dataset[PhotoAmt == 3 , .N/7684,]
dataset[PhotoAmt == 4 , .N/7684,]
dataset[PhotoAmt == 5 , .N/7684,]

dataset[PhotoAmt != 0 , .N/7684,]

```

Time for some boxplots. Let's see how valuable are our numeric variables
```{r}
boxplot(dataset$Age~dataset$y) # Not extremely helpful. The "not adopted" category is slightly older, but not enough. 

boxplot(dataset$Quantity~dataset$y) #This is a bad variable, so obviously it is also bad here. In general it seems people are less inclined to adopt pets in groups, which makes sense. 

boxplot(dataset$Fee~dataset$y) # Really not helpful. Again, we will turn this into a binary variable and see if that makes a difference. 

boxplot(dataset$VideoAmt~dataset$y) #Same as Fee. 

boxplot(dataset$PhotoAmt~dataset$y) # It seems more photos are slightly helpful for increasing the odds for adoption, but only slightly. 
```

Let's make sure we only have NA on secondary variables
```{r}
cleandata <- dataset
cleandata[is.na(cleandata),] <- 0  #SWAP ALL NA TO 0
cleandata <-  cleandata[complete.cases(cleandata), ] #clearrows with NA

cleandata [is.na(Type),.N] # I ran this line of code 20 times, for each variable manually, because I couldn't figure out how to do it more efficiantly. 
```

Indeed that is the case, so we can replace every NA with 0
```{r}
# Again, couldn't figure out a better way. I go through each column and change only the NA with 0. 
for (i in names(cleandata)) {
  cleandata[is.na(get(i)), (i):=0] 
} 
```

Creating the new binary variables from Variables that are currently extremely odd shaped and unhelpful. Also removing old ones.
```{r}
cleandata[,HasFee := ifelse(Fee>0,1,0), ] #84% of pets don't have adoption fee. In order for the those who have fees those who have fees to become a meaningful group we are turning this Binary

cleandata[,HasVideos := ifelse(VideoAmt>0,1,0), ] #96% of pets don't have videos on their profiles. This is why it is more interesting to ask if having videos at all make any difference, hence we turn this Binary as well. 
cleandata[,SingleAdoption := ifelse(Quantity==1,1,0), ]
cleandata <- cleandata [,-'Fee',]
cleandata <- cleandata [,-'VideoAmt',]
cleandata <- cleandata [,-'Quantity',]
```

Connections/correlation between variables
```{r}
cleandata %>% names

table(cleandata$y,cleandata$HasFee) %>% prop.table
chisq.test(cleandata$y,cleandata$HasFee)

mosaicplot(table(cleandata$Sterilized,cleandata$Vaccinated,cleandata$Dewormed), color = T, main = 'Sterilized, Vaccinated, Dewormed MosaicPlot')
mosaicplot(table(cleandata$Sterilized,cleandata$y), color = T)

```

